---
title: "bone_ANOVAs"
author: "Tom"
date: "May 11, 2018"
output: html_document
---

# Load Libraries

```{r}
library(tidyverse)
library(datasets)
library(writexl)
library(broom)
```


## Generate data sets

The toothgrowth dataset has two treatments (Vitamin C and OJ, with 3 doses), doesn't EXACTLY match your criteria

```{r}
# Generate the data, creating multiple fake Dependent Variables
bone_df <- as.tibble(ToothGrowth) %>% 
    mutate(dose = factor(dose),
           molars = len*2,
           crunchers = len*3,
           canines = len*3.14,
           femur = len*37) %>% 
    select(supp, dose, everything())

# for playing around with if you wanna run ONE aov and tukey.
bone_len <- bone_df %>% 
    select(dose, supp, len)

bone_molars <- bone_df %>% 
    select(dose, supp, molars)

bone_crunchers <- bone_df %>% 
    select(dose, supp, crunchers)
```

```{r}
# exploratory graph
bone_df %>% 
    ggplot(aes(x = dose, y = femur)) +
    geom_boxplot() +
    facet_grid(~supp)
```
## Setup and run the ANOVAs

Notice I am selecting ALL the dependent variables since I have one wide dataset with unchanging factors. We do this with our "master" data file that has all of our dependent variables in an individual column with matching factors/ids. This is also how I set up the dataset for this experiment. You can run how ever many dependent variables you wanted as long as they are IN the dataset.

```{r}
# select the depedent variables of interest(exclude the factors)
all_anova <- bone_df %>% 
    select(len:femur) %>% 
    map(~ aov(lm(.x ~ supp * dose, data = bone_df)))

all_anova 
# notice there is a list of dataframes, where each dataset is named after
# the initial column name. You could select from this list of dfs with all_anova$name

# and the broom::tidy output as example
tidy(all_anova$len)

# quick chec to show you what the TukeyHSD looks like 
# we need to specify the interaction with which = 
tidy(TukeyHSD(all_anova$len, which = "supp:dose"))
```


We can now do a few things! I map broom::tidy() to get a nice clean output, round p value to 5 decimal places, and generate a "SIG" or blank if not significant. You can either stack the dataframe with bind_rows and then save as a .csv, .xlsx, or even just keep as a RDS file. 

```{r}
# this does all the nice things and ends up with one LONG dataframe 
# with a label for each set of main effects/interactions/residuals.
all_anova %>% 
    map(., broom::tidy) %>% 
    map(~ mutate(.x, p.value = round(p.value, 5))) %>%
    map( ~ mutate(.x, sig = case_when(p.value <= 0.05 ~ "SIG",
                                  p.value > 0.05 ~ ""))) %>%
    bind_rows(.id = "source")
```


You can do the same thing as above with a `map_dfr` call as well, just make sure to use `.id = "source"` so that you keep the names from list of dataframes.

```{r, eval = F}
all_anova %>% 
    map(., broom::tidy) %>% 
    map(~ mutate(.x, p.value = round(p.value, 5))) %>%
    map_dfr(~ mutate(.x, sig = case_when(p.value <= 0.05 ~ "SIG",
                                  p.value > 0.05 ~ "")), .id = "source")
```

Alternatively I save to indivdual tabs of an excel file, as this is what my boss typically wants to see. Since this is a named list of dataframes, we get nice named tabs on the excel sheet.

```{r}
# this does all the nice things and ends up writing the list of dataframes
# to individuals tabs of an excel file 
all_anova %>% 
    map(., broom::tidy) %>% # notice that map(., tidy) is same as map(~ tidy(.))
    map(~ mutate(.x, p.value = round(p.value, 5))) %>%
    map(~ mutate(.x, sig = case_when(p.value <= 0.05 ~ "SIG",
                                  p.value > 0.05 ~ ""))) %>%
    writexl::write_xlsx(., "bone_anovas_type3.xlsx")

```

## Tukey post-hocs

Now that we have our ANOVAs taken care of, we can run our post-hocs on the ANOVAs. You can either bind into one LONG dataframe (like before w/ anova), or you can bind columns with `map_dfc`, or keep as a list and write to excel.


```{r}
# long dataframe
all_anova %>% 
    map(~ tidy(TukeyHSD(., which = 'supp:dose'))) %>% 
    bind_rows(.id = "source")
```

```{r}
# wide - less than ideal as I don't know a way to generate proper names
# it just will add a number to each of the columns.
all_anova %>% 
    map_dfc(~ tidy(TukeyHSD(., which = 'supp:dose')))
```

```{r}
# write to excel
all_anova %>% 
    map(~ tidy(TukeyHSD(., which = 'supp:dose'))) %>% 
    writexl::write_xlsx(., "tidy_tukey.xlsx")
```

